Econ Modeling One-pager

### 2016-08-08 NSF-ClusterGrant/EconOnePager.Rmd
New paragraph.

One challenge in this work is the computational difficulty involved in fitting CES models 
and quantifying the precision of the estimated parameters that result.  Because of 
numerical challenges, we fit each model with multiple non-linear optimization algorithms,
and because of boundary issues, we explicity refit models along boundaries.  Then, because
parameter precision is challenging to estimate using standard methods, we employ 
computationally intensive resampling and/or Bayesian models.  Our current exploration
is a sort of pilot study considering a limited number of countries, a limited number of 
modeling choices and reducing the number of resamples to an amount that can be readily handled 
on our current hardware in a few hours.  Further work in this area, especially any simulations
to explore the quality of the bootstrap resampling or Bayesian estimation, would require days 
to run currently.
Futhermore, we already have data from several additional countries that we would like to
anaylze by similar methods.

>>>>

One challenge in this work is the computational difficulty involved in fitting CES models 
and quantifying the precision of the estimated parameters that result.  Because of 
numerical challenges, we fit each model with multiple non-linear optimization algorithms,
and because of boundary issues, we explicity refit models along boundaries.  Then, because
estimating parameter precision is challenging using standard methods, we employ 
computationally intensive resampling and/or Bayesian models.  Our current exploration
is a sort of pilot study considering a limited number of countries, a limited number of 
modeling choices and reducing the number of resamples to an amount that can be readily handled 
on our current hardware in a few hours.

Our plans for future work will require significantly-improved computational capabilities.
Each of our planned activities below will require days to run on existing hardware.

* We have in hand data from several additional countries that we would like to
anaylze by similar methods as discussed above.

* We want to explore the quality and performance
of the bootstrap resampling and/or Bayesian estimation techniques.

* Our collaborators in Portugal have completed a paper that uses the 
Cobb-Douglas APF in combination with co-integration techniques to understand
the relationship between energy and the economy in Portugal. 
At the Second Exergy Economics Workshop (Sussex, England)
